---
title: "02 data_analysis"
author: "Fabienne Kock"
date: "13 6 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


packages
```{r}
library(tidyverse)
library(effsize)
library(dplyr)
library(readr)
library(tidyr)
library(DescTools)
library(Rmisc)
```

## 1. read in the data
```{r}
trust_data <- read_csv("C:\\Users\\User\\Documents\\Semester4\\Psychology Lab\\XPLabFinal\\data\\03 paper\\clean\\S1_trust_data.csv")
dom_data <- read_csv("C:\\Users\\User\\Documents\\Semester4\\Psychology Lab\\XPLabFinal\\data\\03 paper\\clean\\S1_Dom_data.csv")
```

## 2. Sensitivity correlation: trust

### 2.0 split data in inverted and transposed
```{r}
upright <- select(trust_data, ID, ends_with("upright"))
inverted <- select(trust_data, ID, ends_with("inverted"))
```
### 2.1 transpose data
```{r}
upright_t <- t(upright)
inverted_t <- t(inverted)
```

```{r}
colnames(upright_t) <- upright_t[1,]
upright_t<-upright_t[-1,]
colnames(inverted_t) <- inverted_t[1,]
inverted_t<-inverted_t[-1,]
```


### 2.2 calculate Pearson correlation
```{r}
pearson <- c()
col <- 1
while(col <= ncol(upright_t)){
  inv <- as.double(inverted_t[,col])
  up <- as.double(upright_t[,col])
  p_val <- cor.test(up,inv,method = "pearson")
  pearson <- c(pearson, toString(p_val)) 
  col <- col+ 1
}
trust_data$pearson <- pearson
```


how it should look like if one does not coerce it into a string
```{r} 
inv <- as.double(inverted_t[,7])
up <- as.double(upright_t[,7])
cor.test(up,inv,method = "pearson")

```

How it looks like in the dataframe
```{r}
trust_data
trust_data$pearson[7]

```
### 2.3 filter out correlation
Function to split the correlation from the information gained by applying Pearson
```{r}
getCorr <- function(row){
  corr <- strsplit(row, ",")
  corr <- corr[[1]]
  corr <- strsplit(corr[4],"=")
  corr <- corr[[1]]
  corr <- strsplit(corr[2],"\\)")
  corr <- corr[[1]]
return(corr)
}
```
Getting the Correlation for every row, adding it as row to the exp_data and converting it back to a numeric
```{r}
corr_list <- c()
row <- 1
while(row <= nrow(trust_data)){
  corr <- getCorr(trust_data$pearson[row])
  corr_list <- c(corr_list, corr)
  row <- row+1
}
```

```{r}
trust_data$Sesnsitivity_correlation <- corr_list
trust_data <- mutate(trust_data, Sensitivity_correlation = as.numeric(corr_list))
```


### 2.4 extract frame with ID pearson, and Sensitivity correlation
```{r}
analysed_trust_data <- select(trust_data, ID, pearson, Sensitivity_correlation)
analysed_trust_data
```
## 3. Sensitivity correlation: dominance

### 3.0 split data in inverted and transposed
```{r}
upright <- select(dom_data, ID, ends_with("upright"))
inverted <- select(dom_data, ID, ends_with("inverted"))
```
### 3.1 transpose data
```{r}
upright_t <- t(upright)
inverted_t <- t(inverted)
```

```{r}
colnames(upright_t) <- upright_t[1,]
upright_t<-upright_t[-1,]
colnames(inverted_t) <- inverted_t[1,]
inverted_t<-inverted_t[-1,]
```


### 3.2 calculate Pearson correlation
```{r}
pearson <- c()
col <- 1
while(col <= ncol(upright_t)){
  inv <- as.double(inverted_t[,col])
  up <- as.double(upright_t[,col])
  p_val <- cor.test(up,inv,method = "pearson")
  pearson <- c(pearson, toString(p_val)) 
  col <- col+ 1
}
dom_data$pearson <- pearson
```


how it should look like if one does not coerce it into a string
```{r} 
inv <- as.double(inverted_t[,7])
up <- as.double(upright_t[,7])
cor.test(up,inv,method = "pearson")

```

How it looks like in the dataframe
```{r}
dom_data
dom_data$pearson[7]

```
### 3.3 filter out correlation
Function to split the correlation from the information gained by applying Pearson
```{r}
getCorr <- function(row){
  corr <- strsplit(row, ",")
  corr <- corr[[1]]
  corr <- strsplit(corr[4],"=")
  corr <- corr[[1]]
  corr <- strsplit(corr[2],"\\)")
  corr <- corr[[1]]
return(corr)
}
```
Getting the Correlation for every row, adding it as row to the exp_data and converting it back to a numeric
```{r}
corr_list <- c()
row <- 1
while(row <= nrow(dom_data)){
  corr <- getCorr(dom_data$pearson[row])
  corr_list <- c(corr_list, corr)
  row <- row+1
}
```

```{r}
dom_data$Sesnsitivity_correlation <- corr_list
dom_data <- mutate(dom_data, Sensitivity_correlation = as.numeric(corr_list))
```


### 3.4 extract frame with ID pearson, and Sensitivity correlation
```{r}
analysed_dom_data <- select(dom_data, ID, pearson, Sensitivity_correlation)
analysed_dom_data
```

## 4 independant sample t-test
### 4.1 filter out necessary data
```{r}
trust <- analysed_trust_data$Sensitivity_correlation
dom <- analysed_dom_data$Sensitivity_correlation
```
### 4.2 visualize with boxplots
```{r}
 boxplot(trust,dom,ylab="correlations of inverted and upright pictures",names=c("trustworthy","dominant"), col=c("tomato","cyan"),boxwex=0.5) 
```
### 4.3 median and standard deviation
```{r}
m_trust <-median(trust)
sd_trust <- sd(trust)
print('Trustworthy', quote = FALSE)
print(c("Median:", m_trust, "Standard deviation:",sd_trust), quote = FALSE)

m_dom <- median(dom)
sd_dom <- sd(dom)
print("Dominance",  quote = FALSE)
print(c("Median:", m_dom, "Standard deviation:",sd_dom), quote = FALSE)


```

###4.4 paired sample t-test
```{r}
t.test(trust,dom)

```

### 4.5cohens d
```{r}
cohen.d(trust, dom)
```

```{r}

```

