---
title: "02 data_analysis"
author: "Fabienne Kock"
date: "13 6 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


packages
```{r}
library(tidyverse)
library(effsize)
library(dplyr)
library(readr)
library(tidyr)
library(DescTools)
library(Rmisc)
```
Function to split the correlation from the information gained by applying Pearson
```{r}
getCorr <- function(row){
  corr <- strsplit(row, ",")
  corr <- corr[[1]]
  corr <- strsplit(corr[4],"=")
  corr <- corr[[1]]
  corr <- strsplit(corr[2],"\\)")
  corr <- corr[[1]]
return(corr)
}
```

## 1. read in the data
```{r}
data <- read_csv("C:\\Users\\User\\Documents\\Semester4\\Psychology Lab\\XPLabFinal\\data\\01 pilot\\S1_data_clean.csv")
data
```
## 1.1 create a df for the results
```{r}
trust <- filter(data, category == "Vertrauenswürdigkeit")
dom <- filter(data, category == "Dominanz")
```


## 2. Sensitivity correlation: Trust

### 2.0 split data in inverted and upright
```{r}
upright_trust <- filter(trust, pictureFormat == "Upright")
inverted_trust <- filter(trust, pictureFormat == "Inverted")
```

### 2.1 calculate Pearson correlation
```{r}
inv <- upright_trust$response
up <- inverted_trust$response
results_trust <- trust %>% 
  group_by(experiment_id) %>% 
  summarize(pearson = cor.test(up,inv,method = "pearson"))
```


how it should look like if one does not coerce it into a string
```{r} 
inv <- upright_trust$response[1]
up <- inverted_trust$response[1]
cor.test(up,inv,method = "pearson")

```

How it looks like in the dataframe
```{r}

results_trust$pearson[1]

```

### 2.2 filter out correlation

Getting the Correlation for every row, adding it as row to the exp_data and converting it back to a numeric
```{r}
corr_list <- c()
row <- 1
while(row <= nrow(results_trust)){
  corr <- getCorr(results_trust$pearson[row])
  corr_list <- c(corr_list, corr)
  row <- row+1
}
```

```{r}
results_trust$Sensitivity_correlation <- corr_list
results_trust <- mutate(results_trust, Sensitivity_correlation = as.numeric(corr_list))
```



## 3. Sensitivity correlation: dominance

### 3.0 split data in inverted and upright
```{r}
upright_dom <- filter(dom, pictureFormat == "Upright")
inverted_dom <- filter(dom, pictureFormat == "Inverted")
```
### 3.1 calculate Pearson correlation
```{r}
inv <- upright_dom$response
up <- inverted_dom$response
results_dom <- dom %>% 
  group_by(experiment_id) %>% 
  summarize(pearson = cor.test(up,inv,method = "pearson"))
```


how it should look like if one does not coerce it into a string
```{r} 
inv <- upright_dom$response[1]
up <- inverted_dom$response[1]
cor.test(up,inv,method = "pearson")

```

How it looks like in the dataframe
```{r}

results_dom$pearson[1]

```



### 3.2 filter out correlation

Getting the Correlation for every row, adding it as row to the exp_data and converting it back to a numeric
```{r}
corr_list <- c()
row <- 1
while(row <= nrow(results_dom)){
  corr <- getCorr(results_dom$pearson[row])
  corr_list <- c(corr_list, corr)
  row <- row+1
}
```
```{r}
results_dom$Sensitivity_correlation <- corr_list
results_dom <- mutate(results_dom, Sensitivity_correlation = as.numeric(corr_list))
```

## 4 independant sample t-test
### 4.1 filter out necessary data
```{r}
trust_cor <- results_trust$Sensitivity_correlation
dom_cor <- results_dom$Sensitivity_correlation
```
### 4.2 visualize with boxplots
```{r}
 boxplot(trust_cor,dom_cor,ylab="correlations of inverted and upright pictures",names=c("trustworthy","dominant"), col=c("tomato","cyan"),boxwex=0.5) 
```
### 4.3 median and standard deviation
```{r}
m_trust <-median(trust_cor)
sd_trust <- sd(trust_cor)
print('Trustworthy', quote = FALSE)
print(c("Median:", m_trust, "Standard deviation:",sd_trust), quote = FALSE)

m_dom <- median(dom_cor)
sd_dom <- sd(dom_cor)
print("Dominance",  quote = FALSE)
print(c("Median:", m_dom, "Standard deviation:",sd_dom), quote = FALSE)


```

###4.4 paired sample t-test
```{r}
t.test(trust,dom)

```

### 4.5cohens d
```{r}
cohen.d(trust, dom)
```

```{r}

```

