---
title: "02 data_analysis"
author: "Fabienne Kock"
date: "13 6 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


packages
```{r}
library(tidyverse)
library(effsize)
library(readr)
library(tidyr)
library(DescTools)
library(Rmisc)
library(broom)
library(purrr)
library(tidyr)
library(dplyr)
library(ggpubr)
library(brms)
```
Function to split the correlation from the information gained by applying Pearson
```{r}
getCorr <- function(row){
  corr <- strsplit(row, ",")
  corr <- corr[[1]]
  corr <- strsplit(corr[4],"=")
  corr <- corr[[1]]
  corr <- strsplit(corr[2],"\\)")
  corr <- corr[[1]]
return(corr)
}
```

## 1. read in the data
```{r}
data <- read_csv("C:\\Users\\User\\Documents\\Semester4\\Psychology Lab\\XPLabFinal\\data\\01 pilot\\S1_data_clean.csv")
data
```
## 1.1 create a df for the results
```{r}
trust <- filter(data, category == "Vertrauenswürdigkeit")
dom <- filter(data, category == "Dominanz")

trust
dom
```


## 2. Sensitivity correlation: Trust

### 2.0 split data in inverted and upright
```{r}
ids <- unique(trust$experiment_id)
trust_list <- list()
for(i in 1:length(ids)){
    id <- ids[i]
    mini.df <- data.frame(trust[trust$experiment_id == id, ])
    trust_list[[id]] <- mini.df
}
```


### 3.1 calculate Pearson correlation

```{r}
pearson_trust <-c()
for(i in trust_list)
    if(! is.null(i)){
    upright <- filter(i, pictureFormat == "Upright")
    inverted <- filter(i, pictureFormat == "Inverted")
    pearson_trust <- c(pearson_trust, toString(cor.test(inverted$response,upright$response,method = "pearson")))
    }
```

### 3.2 filter out correlation

Getting the Correlation for every row, adding it as row to the exp_data and converting it back to a numeric
```{r}
Sensitivity_correlation_trust <- c()

for(elem in pearson_trust){
  corr <- getCorr(elem)
  Sensitivity_correlation_trust <- c(Sensitivity_correlation_trust, corr)
}
```
```{r}
Sensitivity_correlation_trust <- as.numeric(Sensitivity_correlation_trust)
Sensitivity_correlation_trust
```


## 3. Sensitivity correlation: dominance

### 3.0 create df for each experiment_id and split data in inverted and upright


```{r}
ids <- unique(dom$experiment_id)
dom_list <- list()
for(i in 1:length(ids)){
    id <- ids[i]
    mini.df <- data.frame(dom[dom$experiment_id == id, ])
    dom_list[[id]] <- mini.df
}
```


### 3.1 calculate Pearson correlation

```{r}
pearson <-c()
for(i in dom_list)
    if(! is.null(i)){
    upright <- filter(i, pictureFormat == "Upright")
    inverted <- filter(i, pictureFormat == "Inverted")
    pearson <- c(pearson, toString(cor.test(inverted$response,upright$response,method = "pearson")))
    }
```

### 3.2 filter out correlation

Getting the Correlation for every row, adding it as row to the exp_data and converting it back to a numeric
```{r}
Sensitivity_correlation_dom <- c()

for(elem in pearson){
  corr <- getCorr(elem)
  Sensitivity_correlation_dom <- c(Sensitivity_correlation_dom, corr)
}
```
```{r}

Sensitivity_correlation_dom <- as.numeric(Sensitivity_correlation_dom)
Sensitivity_correlation_dom
```


## 4 independant sample t-test
### 4.1 filter out necessary data
```{r}
trust_cor <- Sensitivity_correlation_trust
dom_cor <- Sensitivity_correlation_dom

my_data <- data.frame( 
                group = rep(c("Trsustworthy", "Dominance"), each = 2),
                cor = c(trust_cor,  dom_cor)
                )
my_data
```



### 4.2 visualize with boxplots
```{r}
ggboxplot(my_data, x = "group", y = "cor", 
          color = "group", palette = c("#00AFBB", "#E7B800"),
        ylab = "Sensitivity Correlation", xlab = "Groups")

```
### 4.3 median and standard deviation
```{r}
dplyr::group_by(my_data, group) %>%
  dplyr::summarise(
    median = median(cor, na.rm = TRUE),
    mean = mean(cor, na.rm = TRUE),
    sd = sd(cor, na.rm = TRUE)
  )


#m_trust <-median(trust_cor)
#sd_trust <- sd(trust_cor)
#print('Trustworthy', quote = FALSE)
#print(c("Median:", m_trust, "Standard deviation:",sd_trust), quote = FALSE)

#m_dom <- median(dom_cor)
#sd_dom <- sd(dom_cor)
#print("Dominance",  quote = FALSE)
#print(c("Median:", m_dom, "Standard deviation:",sd_dom), quote = FALSE)


```

###4.4 shapoiro test
```{r}
shapiro.test(trust_cor)
shapiro.test(dom_cor)
```
###4.5 F-test
```{r}
var.test(cor ~ group, data = my_data)
```


### 4.6 independant sample t-test
```{r}
t.test(trust_cor,dom_cor, alternative = "two.sided", var.equal = FALSE)
```
whether the average dominance correlation is less than the average trust correlation
```{r}
t.test(cor ~ group, data = my_data,
        var.equal = TRUE, alternative = "less")
```

### 4.5 cohens d
```{r}
cohen.d(trust_cor, dom_cor, alternative = "two.sided", var.equal = FALSE)
cohen.d( dom_cor, trust_cor, alternative = "two.sided", var.equal = FALSE)
```

-> bayesian regression between Dominanz and Trustworthyness
```{r}
model_1 <- brm(formula = response ~ category, family = "cumulative", data = data)
```
```{r}
model_2<- brm(formula = response ~ category + pictureFormat, family = "cumulative", data = data)
```
```{r}
model_3 <- brm(formula = response ~ category + (category|pictureFormat), family = "cumulative", data = data)
model_3
```

```{r}
model_4 <- brm(formula = response ~ category + (1|experiment_id), family = "cumulative", data = data)
```

```{r}
model_5 <- brm(formula = response ~ category + pictureFormat + (1|experiment_id), family = "cumulative", data = data)
```

```{r}
model_6 <- brm(formula = response ~ category + (category|pictureFormat) + (1|experiment_id), family = "cumulative", data = data)
```

```{r}
model_1
model_2
loo1 <-loo(model_1)
loo2 <-loo(model_2)
```
```{r}
loo1
loo2
```

```{r}

loo_compare(loo1,loo2)
```

